---
title: "Davidson"
author: "Stephenson"
date: "2024-01-28"
output: html_document
---

```{r}
library(readxl)
library(dplyr)
library(tidyverse)
library(tidyr)
library(readr)
library(openxlsx)
```


#Import data

```{r}
AM<- read_xlsx("MeteoRigaUniversity_Cleaned2.xlsx")
```

```

```{r}
# Convert 'Date' column to Date type
AM$Date <- as.Date(AM$Date, format = "%d.%m.%Y")
```


#Firsttwins
```{r}
# Add a Week column starting from January 1st of each year
dftest <- AM %>% mutate(
  Year = lubridate::year(Date),
  StartOfYear = as.Date(paste(Year, "-01-01", sep = ""), format = "%Y-%m-%d"),
  Week = ceiling(as.numeric(Date - StartOfYear + 1) / 7)
)%>% 
select(-StartOfYear)
```




```{r}
# Calculate weekly payments
# Calculate weekly Sums
weekly_Sum <- dftest %>%
  group_by(Year, Week) %>%
  summarize( Temperaturesum = sum(Temperature,  na.rm = TRUE), Windspeedsum = sum(Windspeed,  na.rm = TRUE),AtmosphericPressuresum = sum(AtmosphericPressure,  na.rm = TRUE),TemperatureGradientsum = sum(TemperatureGradient,  na.rm = TRUE))
```




```{r}
# Merge the weekly payments back to the original dataframe
#result_df22 <- merge(dftest, weekly_Sum, by = c("Year", "Week"), all.x = TRUE)
```

 


# Count all values (including NA) in the 'Ķengarags' column by Weekly ID

```{r}
count_by_id <- result_df22 %>%
  group_by(Week, Year) %>%
  summarise(Total_Values_Weekly = n())
```






```{r}
# #Count all values (excluding NA) in theTemeprature' Weekly ID
Temperature_NotNA<- result_df22 %>%
  group_by( Week, Year) %>%
  summarize(Temperature_NotNA = sum(!is.na(Temperature)))

```



```{r}
# #Count all values (excluding NA) in Windspeed Weekly ID
Windspeed_NotNA<- result_df22 %>%
  group_by( Week, Year) %>%
  summarize(Windspeed_NotNA = sum(!is.na(Windspeed)))

```






```{r}
# #Count all values (excluding NA) in theTemeprature' Weekly ID
AtmosphericPressure_NotNA<- result_df22 %>%
  group_by( Week, Year) %>%
  summarize(AtmosphericPressure_NotNA = sum(!is.na(AtmosphericPressure)))

```



```{r}
# #Count all values (excluding NA) in Windspeed Weekly ID
TemperatureGradient_NotNA<- result_df22 %>%
  group_by( Week, Year) %>%
  summarize(TemperatureGradient_NotNA = sum(!is.na(TemperatureGradient)))

```









#SPECIALZONE(WeeklyformatArena:  SECONDSHEETDATA)






```{r}
# Create a list of your data frames
data_frames <- list(Windspeed_NotNA, Temperature_NotNA, TemperatureGradient_NotNA, AtmosphericPressure_NotNA, weekly_Sum,count_by_id)

# Define the columns by which you want to merge
merge_cols <- c("Week", "Year")

# Merge the data frames using Reduce function
merged_df <- Reduce(function(x, y) merge(x, y, by = merge_cols, all = TRUE), data_frames)

```









```{r}
TESTBB <- merged_df %>% 
  mutate(
    Averageweekly_Temperature = Temperaturesum/Temperature_NotNA, Averageweekly_Windspeed = Windspeedsum/Windspeed_NotNA, Averageweekly_TemperatureGradientsum = TemperatureGradientsum/TemperatureGradient_NotNA, Averageweekly_AtmosphericPressuresum = AtmosphericPressuresum/AtmosphericPressure_NotNA)
    
    

```





#EXPORTINGSHEETZONE


```{r}
# Install and load the openxlsx package
#install.packages("openxlsx")
library(openxlsx)

# Specify the Excel file path
excel_file <- "C:/Users/Stephen/Desktop/Davidsonproject/okay/MetroRegaAverageweekly_detailed.xlsx"

# Write the data frame to Excel
write.xlsx(TESTBB, excel_file)

```





